Precise predictions for same-sign W-boson scattering at the LHC

### 2018-03-19 Draft_arXiv/article.tex
small fixes in the draft

  Vector-boson scattering processes are of great importance for the
  current run-II and future runs of the Large Hadron
  Collider. The presence of triple and quartic gauge couplings in the
  process gives access to the gauge sector of the Standard Model (SM) and
  possible new-physics contributions there.  To test this hypothesis,
  sound knowledge of the SM contributions is necessary,
  with a precision which at least matches the experimental
  uncertainties of existing and forthcoming measurements.  In this
  article we present a detailed study of the vector-boson scattering
  process with two positively-charged leptons and missing transverse
  momentum in the final state. In particular,
  we first carry out a systematic comparison of the various
  approximations that are usually performed for this kind of process
  against the complete calculation, at LO and NLO QCD accuracy. Such a
  study is performed both in the usual fiducial region used by
  experimental collaborations and in a more inclusive phase space,
  where the differences among the various approximations lead to more
  sizeable effects.  Afterwards, we turn to predictions
  matched to parton showers, at LO and NLO: we show that on the one
  hand, the inclusion of NLO QCD corrections leads to more stable
  predictions, but on the other the details of the matching and of the
  parton-shower programs cause differences which are considerably
  larger than those observed at fixed order, even in the experimental
  fiducial region.  We conclude with some recommendations for
  experimental studies of vector-boson scattering processes.\\[5mm]

@@

Finally, the third contribution is the interference of the two types of amplitudes described above.
It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
Such a contribution is typically small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.

@@

      \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space phase corresponding to the real emission.
    For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.

>>>>

  Vector-boson scattering processes are of great importance for the
  current run-II and future runs of the Large Hadron
  Collider. The presence of triple and quartic gauge couplings in the
  process gives access to the gauge sector of the Standard Model (SM) and
  possible new-physics contributions there.  To test any new-physics hypothesis,
  sound knowledge of the SM contributions is necessary,
  with a precision which at least matches the experimental
  uncertainties of existing and forthcoming measurements.  In this
  article we present a detailed study of the vector-boson scattering
  process with two positively-charged leptons and missing transverse
  momentum in the final state. In particular,
  we first carry out a systematic comparison of the various
  approximations that are usually performed for this kind of process
  against the complete calculation, at LO and NLO QCD accuracy. Such a
  study is performed both in the usual fiducial region used by
  experimental collaborations and in a more inclusive phase space,
  where the differences among the various approximations lead to more
  sizeable effects.  Afterwards, we turn to predictions
  matched to parton showers, at LO and NLO: we show that on the one
  hand, the inclusion of NLO QCD corrections leads to more stable
  predictions, but on the other the details of the matching and of the
  parton-shower programs cause differences which are considerably
  larger than those observed at fixed order, even in the experimental
  fiducial region.  We conclude with some recommendations for
  experimental studies of vector-boson scattering processes.\\[5mm]

@@

Finally, the third contribution is the interference of the two types of amplitudes described above.
It is non-zero only for those partonic sub-processes which involve identical quarks or anti-quarks.
Such a contribution is normally small ($3\%$) within typical experimental cuts~\cite{Biedermann:2017bss}.

@@

      \item The {\sc Powheg-Box}~\cite{Nason:2004rx,Frixione:2007vw,Alioli:2010xd} is a framework for matching NLO-QCD calculations with parton showers.
    It relies on the user providing the matrix elements and Born phase space, but automatically constructs FKS \cite{Frixione:1995ms} subtraction terms and the phase space corresponding to the real emission.
    For the VBS processes all matrix elements are being provided by a previous version of {\sc VBFNLO}~\cite{Arnold:2008rz, Arnold:2011wj, Baglio:2014uba} and hence the approximations used in the {\sc Powheg-Box} are similar to those used in {\sc VBFNLO}.
